Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-04 be.tex
appendix B3

Combining equations~\eqref{eq:enConsInt} and \eqref{eq:massFlux} with the result of equation \eqref{eq:Phi}, we obtain 
\begin{align}
  &\mathcal{B} = -U_o\left[\frac{\rs/\rb}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
  &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
  \frac{1-2\delta}{2(\delta+1)} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
  \nonumber\\
  &-\frac{G M_\star}{r_s}
  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
\end{align}
where $U_o=4 \pi G \rhostar(\rs) \rs^2$.  We may rewrite this as

\begin{multline}
  \mathcal{B} =\frac{G \Mbh}{\rs} 
\biggl[
  \frac{3}{2} \zeta^2 w^{\frac{1}{3 -\delta}}
  -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
  -\frac{\rb}{\rsoi} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2 -\delta} 
  -w \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
\biggr],
\label{eq:enthAnal}
\end{multline}
where $\zeta \equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$ and $w\equiv (\rs/\rsoi)^{3\delta}$, and
$\delta$ is the power law slope of the stellar density profile inside
of the break radius, $\rb$.

When the rate of external heating is high, we have $\mathcal{B} > 0$ at all radii, requiring an outflow.  As heating ($\zeta$) is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ first becomes negative.  If $\zeta<\zeta_c$, then there is a minimum value of $\rs/\rsoi$, $(\rs/\rsoi)_{\rm min}$, above which we have $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive kinetic energy at infinity.  The value of $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).  Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of
Fig.~\ref{fig:zetaCrit}). Likewise $(r_{\rm s}/r_{b})_{\rm min}$ is an increasing function of $\zeta/\zeta_{c}$, approaching unity for $\zeta < 0.5\zeta_c$ {\bf BDM: put in the right numbers here}.  For values of $\zeta<\zeta_c$, the stagnation radius rapidly approaches the break radius as shown in the
bottom panel of Fig.~\ref{fig:zetaCrit}.

>>>>

Combining equations~\eqref{eq:enConsInt} and \eqref{eq:massFlux} with the result of equation \eqref{eq:Phi}, we obtain 
\begin{align}
  &\mathcal{B} = -U_o\left[\frac{\rs/\rb}{2-\delta}-\frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{(5-2\delta)(2-\delta)}\right]\nonumber\\
  &+\frac{v_w^2}{2}+\frac{\sigma_0^2}{2}- \frac{G \Mbh}{r_s}
  \frac{1-2\delta}{2(\delta+1)} \frac{3-\delta}{2-\delta}\frac{x^{2-\delta}-1}{x^{3-\delta}-1}
  \nonumber\\
  &-\frac{G M_\star}{r_s}
  \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}\frac{3-\delta}{5-2\delta},
\end{align}
where $U_o=4 \pi G \rhostar|_{\rs} \rs^2$.  This can be rewritten as
\begin{multline}
  \mathcal{B} =\frac{G \Mbh}{\rs} 
\biggl[
  \frac{3}{2} \zeta^2 w^{\frac{1}{3 -\delta}}
  -\frac{(1-2\delta)(3-\delta)}{2(\delta+1)(2-\delta)}  \frac{x^{2  -\delta}-1}{x^{3-\delta}-1}\\
  -\frac{\rb}{\rsoi} w^{\frac{\delta-1}{3-\delta}} \frac{3 -\delta}{2 -\delta} 
  -w \frac{(2-\delta)(3-\delta)-(3-\delta)^{2}}{(5-2\delta)(2-\delta)} \frac{x^{5-2\delta}-1}{x^{3-\delta}-1}
\biggr],
\label{eq:enthAnal}
\end{multline}
where $\zeta \equiv \sqrt{v_w^2+\sigma_0^2}/\sigma_0$ and $w\equiv (\rs/\rsoi)^{3\delta}$, and
$\delta$ is the power law slope of the stellar density profile inside
of the break radius, $\rb$.

When the rate of external heating is high ($\zeta \gg 1$), we have $\mathcal{B} > 0$ at all radii, requiring an outflow.  As $\zeta$ is decreased, there exists a critical value of $\zeta = \zeta_{c}$ below which $\mathcal{B}$ becomes negative near the stagnation radius.  If $\zeta<\zeta_c$, then there is a minimum value of $\rs/\rsoi$, $(\rs/\rsoi)_{\rm min}$, above which we have $\mathcal{B} > 0$ at the break radius, allowing an outflow with positive kinetic energy at infinity.

The value of $\zeta_c$ is an increasing function of $r_{b}/r_{\rm soi}$ and is larger for core galaxies than cusp galaxies, since a greater heating rate is required to unbind gas from a deeper stellar potential (Fig.~\ref{fig:zetaCrit}).  Specifically, we find $\zeta_c\sim (\rb/\rsoi)^{0.5(1-\Gamma)}$ for $\rb\gsim\rsoi$ (see the top panel of
Fig.~\ref{fig:zetaCrit}). Likewise $(r_{\rm s}/r_{b})_{\rm min}$ is an increasing function of $\zeta/\zeta_{c}$, approaching unity for $\zeta < 0.5\zeta_c$ {\bf BDM: put in the right numbers here}.  For values of $\zeta<\zeta_c$, the stagnation radius rapidly approaches the break radius as shown in the
bottom panel of Fig.~\ref{fig:zetaCrit}.
